---
title: "Cleaning the GPS Data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/RWorkingDirectory")
```

## Subsetting by Range & Individual Sheep ID

First, I uploaded the GPS data. I checked for duplicates - there were none. Then, I subset the data for only the mountain ranges that I am interested in: South Bristols (BrsS), Marbles (Marb), Nopah (Nopa), Castle-Piute (CMPR), and Newberry-Rodman-Ord (NROM). Then I subset to only the individual bighorn that I am interested in - those with fix rates of 4 hours or less.

```{r}
library(rmarkdown)
setwd("~/RWorkingDirectory")

# This doesn't work in R Markdown for some reason. Why?
allgpsdata <- read.csv("AllGPSData20190501to20190912.csv", header = TRUE, sep = ",")
View(allgpsdata)
str(allgpsdata)
library(tidyverse)
summary(duplicated(allgpsdata))
rangegpsdata <- allgpsdata[allgpsdata$MountainRange == "BrsS" | allgpsdata$MountainRange == "Marb" | allgpsdata$MountainRange == "Nopa" | allgpsdata$MountainRange == "CMPR" | allgpsdata$MountainRange == "NROM", ]
View(rangegpsdata)
str(rangegpsdata)
rangegpsdata$BHSID <- as.factor(rangegpsdata$BHSID)
# This does not take into account the Castle-Piute sheep being in the wrong place or the question of the NROM sheep. All possible sheep with 1 or 4 hour fix rates are included.
rangeidgpsdata <- rangegpsdata[rangegpsdata$BHSID == "1581" | rangegpsdata$BHSID == "1589" |rangegpsdata$BHSID == "1595" | rangegpsdata$BHSID == "1584" | rangegpsdata$BHSID == "1588" | rangegpsdata$BHSID == "1582" | rangegpsdata$BHSID == "1577" | rangegpsdata$BHSID == "1683" | rangegpsdata$BHSID == "1682" | rangegpsdata$BHSID == "1684" | rangegpsdata$BHSID == "1688" | rangegpsdata$BHSID == "1685" | rangegpsdata$BHSID == "1689" | rangegpsdata$BHSID == "1687" | rangegpsdata$BHSID == "1580" | rangegpsdata$BHSID == "1686" | rangegpsdata$BHSID == "1568" | rangegpsdata$BHSID == "1565" | rangegpsdata$BHSID == "1567" | rangegpsdata$BHSID == "1564" | rangegpsdata$BHSID == "1677" | rangegpsdata$BHSID == "1563" | rangegpsdata$BHSID == "1727" | rangegpsdata$BHSID == "1731" | rangegpsdata$BHSID == "1730" | rangegpsdata$BHSID == "1733" | rangegpsdata$BHSID == "1736" | rangegpsdata$BHSID == "1738" | rangegpsdata$BHSID == "1740" | rangegpsdata$BHSID == "1739", ]
View(rangeidgpsdata)
```

## Subsetting to every four hour

To remove the locations that were taken at 20 minute fix rates, I subset by the rows where the minutes were between 55 and 10. The number of rows before subsetting was `r nrow(rangeidgpsdata` while the number of rows after subsetting was `r nrow(rangeidhour)`, demonstrating that rows with locations taken not close to the hour mark were removed. 

After double checking that all the four-hour collars were on the same schedule, I then subset the gps data to only the rows where the hours were 00, 04, 08, 12, 16, and 20. This reason for this subsetting was to make all the collars be on the same, four hour schedule in order to make them comparable.

```{r}

rangeidgpsdata$TimeLocal <- as.character(rangeidgpsdata$TimeLocal)
rangeidgpsdata$DateTimeLocalTest <- rangeidgpsdata$DateTimeLocal
library(lubridate)

rangeidgpsdata$DateTimeLocalTest <- strptime(rangeidgpsdata$DateTimeLocalTest, "%m/%d/%Y %H:%M")
rangeidgpsdata$DateTimeLocalTestct <- as.POSIXct(rangeidgpsdata$DateTimeLocalTest, tz = "America/Los_Angeles", format = "%m/%d/%Y %H:%M")
rangeidhour <- subset(rangeidgpsdata, format(rangeidgpsdata$DateTimeLocalTest, "%M") %in% c('00', '01', '02', '03', '04', '05', '06', '07', '08', '09', '10', '55', '56', '57', '58', '59', '54', '53', '52', '51', '50'))
## Double check the ones that are every four hours to make sure that they are on a 0-4-8-12-16-20-24 schedule. Do this using summary - starting at NROM 1564E.
rangeidfourhour <- subset(rangeidhour, format(rangeidhour$DateTimeLocalTest, "%H") %in% c('00', '04', '08', '12', '16', '20', '24'))


```
I next subset the data to the time periods that I had camera data for. Due to not covering the creek at the bottom of the Castle Piutes, and realizing at the end of the summer that bighorn go back and forth between this creek and Paiute Guzzler, I decided to limit my analysis of the Castle Piutes to the mine area. This means that the Castle Piute dates are only for Hart Mine tank, Hart Mine Cattails, Kidney Spring Tank, and Kidney Spring Seep.

Marbles: 
2019-05-17 10:49:00 - 2019-05-25 00:00:00
2019-06-04 20:00:00 - 2019-06-12 13:32:00
2019-06-18 17:19:00 - 2019-06-23 00:00:00
2019-06-25 14:49:00 - 2019-06-30 10:46:00
2019-07-10 08:45:00 - 2019-07-13 23:00:18
2019-07-17 11:46:00 - 2019-07-25 10:30:00
2019-07-31 20:52:00 - 2019-08-04 13:13:03
2019-08-06 12:03:00 - 2019-08-10 12:03:23

South Bristols:
2019-06-04 15:04:00 - 2019-06-16 08:27:00
2019-06-18 17:36:00 - 2019-06-25 16:25:00
2019-06-25 17:05:00 - 2019-07-29 10:36:00
2019-08-01 14:32:00 - 2019-08-12 11:13:00

Castle Piute:
2019-05-23 15:48:00 - 2019-05-31 11:18:00
2019-06-20 17:47:00 - 2019-06-27 02:09:00
2019-07-11 18:25:00 - 2019-07-14 18:28:00
2019-07-30 14:30:00 - 2019-08-03 16:46:00
2019-08-05 19:10:00 - 2019-08-15 07:27:00

Nopah:
2019-06-06 09:18:00 - 2019-06-13 11:04:00
2019-06-25 09:00:00 - 2019-07-08 12:35:00
2019-07-16 19:03:00 - 2019-07-29 15:06:00
2019-07-29 19:55:00 - 2019-08-07 14:49:00

Also due to the lack of coverage in the Castle Piutes, I limited the analysis to bighorn that located in the mine area (1730, 1733). I also cut the time period of 1731, who located throughout the range, to time periods when he was found within the mine area. 1731 was not included in the vistation analysis because of this.

Also have to figure out South Nopah vs. rest of Nopahs

```{r}
marbfourhour <- rangeidfourhour[rangeidfourhour$MountainRange == "Marb", ]
marbcutfourhour <- marbfourhour[(marbfourhour$DateTimeLocalTestct >= as.POSIXct("2019-05-17 10:49:00") & marbfourhour$DateTimeLocalTestct <= as.POSIXct("2019-05-25 00:00:00")) | (marbfourhour$DateTimeLocalTestct >= as.POSIXct("2019-06-04 20:00:00") & marbfourhour$DateTimeLocalTestct <= as.POSIXct("2019-06-12 13:32:00")) | (marbfourhour$DateTimeLocalTestct >= as.POSIXct("2019-06-18 17:19:00") & marbfourhour$DateTimeLocalTestct <= as.POSIXct("2019-06-23 00:00:00"))| (marbfourhour$DateTimeLocalTestct >= as.POSIXct("2019-06-25 14:49:00") & marbfourhour$DateTimeLocalTestct <= as.POSIXct("2019-06-30 10:46:00"))| (marbfourhour$DateTimeLocalTestct >= as.POSIXct("2019-07-10 08:45:00") & marbfourhour$DateTimeLocalTestct <= as.POSIXct("2019-07-13 23:00:18")) | (marbfourhour$DateTimeLocalTestct >= as.POSIXct("2019-07-17 11:46:00") & marbfourhour$DateTimeLocalTestct <= as.POSIXct("2019-07-25 10:30:00")) | (marbfourhour$DateTimeLocalTestct >= as.POSIXct("2019-07-31 20:52:00") & marbfourhour$DateTimeLocalTestct <= as.POSIXct("2019-08-04 13:13:03")) | (marbfourhour$DateTimeLocalTestct >= as.POSIXct("2019-08-06 12:03:00") & marbfourhour$DateTimeLocalTestct <= as.POSIXct("2019-08-10 12:03:23")), ]

sbrsfourhour <- rangeidfourhour[rangeidfourhour$MountainRange == "BrsS", ]
sbrscutfourhour <- sbrsfourhour[(sbrsfourhour$DateTimeLocalTestct >= as.POSIXct("2019-06-04 15:04:00") & sbrsfourhour$DateTimeLocalTestct <= as.POSIXct("2019-06-16 08:27:00")) | (sbrsfourhour$DateTimeLocalTestct >= as.POSIXct("2019-06-18 17:36:00") & sbrsfourhour$DateTimeLocalTestct <= as.POSIXct("2019-06-25 16:25:00")) | (sbrsfourhour$DateTimeLocalTestct >= as.POSIXct("2019-06-25 17:05:00") & sbrsfourhour$DateTimeLocalTestct <= as.POSIXct("2019-07-29 10:36:00")) | (sbrsfourhour$DateTimeLocalTestct >= as.POSIXct("2019-08-01 14:32:00") & sbrsfourhour$DateTimeLocalTestct <= as.POSIXct("2019-08-12 11:13:00")),]
  
cmprfourhour <- rangeidfourhour[rangeidfourhour$MountainRange == "CMPR", ]
cmprcutfourhour <- cmprfourhour[(cmprfourhour$DateTimeLocalTestct >= as.POSIXct("2019-05-23 15:48:00") & cmprfourhour$DateTimeLocalTestct <= as.POSIXct("2019-05-31 11:18:00")) | (cmprfourhour$DateTimeLocalTestct >= as.POSIXct("2019-06-20 17:47:00") & cmprfourhour$DateTimeLocalTestct <= as.POSIXct("2019-06-27 02:09:00")) | (cmprfourhour$DateTimeLocalTestct >= as.POSIXct("2019-07-11 18:25:00") & cmprfourhour$DateTimeLocalTestct <= as.POSIXct("2019-07-14 18:28:00")) | (cmprfourhour$DateTimeLocalTestct >= as.POSIXct("2019-07-30 14:30:00") & cmprfourhour$DateTimeLocalTestct <= as.POSIXct("2019-08-03 16:46:00")) | (cmprfourhour$DateTimeLocalTestct >= as.POSIXct("2019-08-05 19:10:00") & cmprfourhour$DateTimeLocalTestct <= as.POSIXct("2019-08-15 07:27:00")),]

nopafourhour <- rangeidfourhour[rangeidfourhour$MountainRange == "Nopa", ]
nopacutfourhour <- nopafourhour[(nopafourhour$DateTimeLocalTestct >= as.POSIXct("2019-06-06 09:18:00") & nopafourhour$DateTimeLocalTestct <= as.POSIXct("2019-06-13 11:04:00")) | (nopafourhour$DateTimeLocalTestct >= as.POSIXct("2019-06-25 09:00:00") & nopafourhour$DateTimeLocalTestct <= as.POSIXct("2019-07-08 12:35:00")) | (nopafourhour$DateTimeLocalTestct >= as.POSIXct("2019-07-16 19:03:00") & nopafourhour$DateTimeLocalTestct <= as.POSIXct("2019-07-29 15:06:00")) | (nopafourhour$DateTimeLocalTestct >= as.POSIXct("2019-07-29 19:55:00") & nopafourhour$DateTimeLocalTestct <= as.POSIXct("2019-08-07 14:49:00")),]

allcutfourhour <- rbind(marbcutfourhour, sbrscutfourhour, cmprcutfourhour, nopacutfourhour)


```
Using CalTopo: 
Marbles: 597' - 3840' (181 m - 1171 m)
South Bristols: 703' - 3269' (214 m - 997 m)
NROM: 1862'-3978' (567 m - 1213 m)
Castle Piute: 2201'-5258' (670 m - 1603 m)
Nopah: 1392'-5249' (424 m - 1599 m)

```{r}

library(rosm)
library(prettymapr)

marbles <- makebbox(34.743890,-115.475526,34.521739,-115.699376)

# n, e, s, w
bmaps.plot(marbles, type = "Aerial", zoom = 10)


# sp package
# talk to Lorena
raster()

library(moveHMM)


# JUNK CODE FROM ATTEMPTS:
# ggmap(get_stamenmap(bbox = c(left = -115.656813, bottom = 34.648079, right = -115.471502, top = 34.639717), maptype = "terrain", crop = FALSE, zoom = 12))

# install.packages("devtools")
# install.packages("ggmap")
# library(ggmap)
# library(ggplot2)
# library("devtools")
# marblesbasemap <- get_map(location = c(lon = 115.582657, lat = 34.641645), zoom = 11, maptype = 'hybrid', source = 'stamen') 

# bbox <- c(left = 34.639717, bottom = 115.471502, right = 34.648079, top = 115.656813)
# ggmap(get_map(bbox, zoom = 13))

# bbox <- get_stamenmap(bbox = c(left = 34.639717, bottom = 115.471502, right = 34.648079, top = 115.656813), maptype = "terrain", crop = FALSE, zoom = 10)

# Attempt #2
# get_map(location = c(lon = -115.571137, lat = 34.636558), zoom = 10, scale = "auto", maptype = "terrain", source = "google")

```



```{r}

raster()
```

